\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-03-10 paper.tex
Section on semantic disambiguation

@@

\cite{Ros2010b}

>>>>

\subsection{Natural language grounding}

@@

One protoypical example of semantic disambiguation has been given in
\cite{Ros2010b} with the child's \emph{spygame}: two players are facing
eachother with a set of random objects inbetween, one player mentally choose
one object, and the other player has to guess the object by asking closed
questions like \emph{Is your object small or large?}. Based on the knowledge it
has acquired, the robot is able to minimize the number of questions required to
find the object.

When playing this kind of game, however, the issue arises that the robot has no
way to select which knowledge about the object is relevant in the interaction
context. For instance, the knowledge base may store facts like \stmt{obj1 type
ActiveConcept} (which internally means that this concept was mentioned in a
discussion in the last few seconds): this information is not a relevant
property of \concept{obj1} when trying to disambiguate concepts with humans.
This distinction between \emph{internal knowledge} (meaningful to
the systme only) and \emph{common knowledge} (whose meaning is understood by
all the interactors) has not been properly dealt with in our architecture.

Besides, even knowledge that belongs to what we call \emph{common knowledge},
may not be appropriate in a given interaction context. For instance, the system
may compute that at a given instant, the human is looking at the object:
\stmt{human looksAt obj1}. This property makes sense to both parties, but in
the context of the \emph{spygame}, we would like to mainly use immanent
properties, not volatile like a gaze. More research is required to precise this
idea of contexts and knowledge class attached to them.
